There once was a grid at ol' Carkeek

### 2016-03-17 Manuscript/carkeek_grid.tex
add site map placeholder

@@

Sidenote justification for k-means clustering: While variation among sampled ecological is indeed continuous, ecologists often apply categorical groupings to ecological communities.
For example, we may sample along a transect that intersects rainforest and desert.
As our samples become smaller and closer together, we may have increasing difficulty assigning samples to a distinct habitat type.

@@

\begin{figure}[h!] % [h!] forces the figure to be placed roughly here
  \centering
    \includegraphics[width=1\textwidth]{site_map.pdf}
    \caption{Geographic position of collected samples. Lines give 10m isobaths.}
  \label{site_map} % use this to refer to your figure in the text, so that numbering updates automatically
\end{figure}

>>>>

\subsection*{Community Analysis}
% Used k-medoids (PAM) rather than k-means because it does not require euclidean distances can be computed and that the observations follow a gaussian distribution
% because of the nature of our data (lots of zeros, with some very high counts), the mean is not very informative
We simultaneously assessed the existence of distinct community types and the membership of samples to those community types using a partitioning around mediods algorithm (CITE PAM, sometimes referred to as k-mediods clustering), as implemented in the R package fpc (CITE fpc).
The classification of samples to communities was made on the basis of their pairwise Bray-Curtis dissimilarity, calculated using the function vegdist in the R package vegan (CITE VEGAN). % consider Gower distance

@@

@@

\begin{figure}[h!] % [h!] forces the figure to be placed roughly here
  \centering
    \includegraphics[width=1\textwidth]{../Figures/site_map.pdf}
    \caption{Geographic position of collected samples. Lines give XXX meter isobaths.}
  \label{site_map} % use this to refer to your figure in the text, so that numbering updates automatically
\end{figure}
